Eagle: multi-locus association mapping on a genome-wide scale made routine

### 2019-08-08 BioinformaticsRevison/bioinformaticspaper.tex
Adding FarmCPU discussion point v2

>>>>

FarmCPU (ref) is a multi-locus association mapping method that was brought to our attention 
by a reviewer. It is different to other linear mixed model approaches in that it makes use of two separate models for analysis, 
a fixed effects model and a random effects model. FarmCPU iterates over these two models. 
The measures of association, obtained from the fixed 
effect model are used to define pseudo-QTN from the fitting of the random effect model. Conversely, by placing the SNP into "bins" and 
optimising the random effects model for bin number and size, pseudo-QTN  are identified and passed back to the fixed effect model. 
It is an intriguing approach.  We were interested in comparing Eagle to FarmCPU so we reanalysed the mouse data with FarmCPU. 
Like Eagle, FarmCPU found 107 SNP-trait associations but the findings were the same for only 11 of the traits. For 14 (14) traits, Eagle (FarmCPU) found more associations.  Furthermore, unlike for Eagle, FarmCPU found X associations that could not be confirmed from the original study's findings. Further work would be needed to determine the true validity of these new results.  An area where the two 
methods differ significantly is in their implementation.  Eagle has been developed for ease-of-use. Eagle is an R package but 
its browser-based GUI makes it accessible to all users.  In contrast,  FarmCPU exists as a set of downloadable R scripts.
